---
title: "Recommender_System"
author:
  - SHIVAM VATS
  - SUSHIL DEORE
  - ANSH SACHDEVA
output: word_document
date: "2022-12-07"
---

#### Question of Interest

What features reflect some pattern that would be usefulto target relevant audience, so that the customer engagement can be increased.

#### Data:
##### Source: Data is taken from Kaggle: https://www.kaggle.com/competitions/airbnb-recruiting-new-user-bookings/data

Dataset is a collection of users along with their demographics, web session  records, and some summary statistics. All the users in this dataset are from the USA. Here is a short description of the features of data:

1. id: user id
2. date_account_created: the date of account creation
3. timestamp_first_active: timestamp of the first activity, note that it can be earlier than date_account_created or date_first_booking because a user can search before signing up
4. date_first_booking: date of first booking
5. gender
6. age
7. signup_method - Platform used for signup
8. signup_flow: the page a user came to signup up from
9. language: international language preference
10. affiliate_channel: what kind of paid marketing
11. affiliate_provider: where the marketing is e.g. google, craigslist, other
12. first_affiliate_tracked: whats the first marketing the user interacted with before the signing up
13. signup_app
14. first_device_type
15. first_browser
16. country_destination

<br>

### Analysis

```{r include=FALSE}
# Importing data
library(ggplot2)
library(tidyverse)
library(dplyr)
library(gridExtra)
```
<br>
Importing data and checking its result
<br>
```{r importing-data}
data <-read.csv("Airbnb New User Bookings.csv")
print(head(data, n = 15))
# Checking dimensions of data
dim(data)
```
<br>
Dropping columns of related to timestamps since it is not relevant and useful in this scenario. 
<br>
```{r}
# dropping id and timestamp related features
data <- data[,-(1:4), drop= FALSE]
```
<br>
Checking for null values
<br>
```{r}
# Checking Column wise null values
colSums(is.na(data))
```

```{r}
# Checking structure of data
str(data)

# Checking summary of data
summary(data)

```
<br>
Distribution of Gender
<br>

```{r}
# Distribution of Gender
ggplot(data, aes(x=gender)) +
  geom_bar(aes(fill=gender))
```
<br>
% missing values in age
<br>
```{r}
# Checking % missing values in column age
sum(is.na(data$age))*100/dim(data)[1]

```
<br>
Summary Statistics of Age
<br>
```{r}
# Checking summary statistics of age
summary(data$age)
```
<br>
From the above statistics, we can see that the maximum value of age is 2014. Hence, we shall remove outliers/errors while analyzing the same
<br>
```{r}
# Removing outliers in age
age_filtered = data %>% filter(age <= IQR(age,na.rm = TRUE)*1.5 + 50)
```
<br>
Distribution of age with respect to gender
<br>
```{r}
plt1 = ggplot(age_filtered,aes(x=age,na.rm=TRUE))+
  stat_density(aes(fill=gender))+
  ggtitle("Distribution of Age with respect to Gender")+
  theme(plot.title = element_text(hjust=0.5))
```

```{r}
# Possible values in Signup method
unique(data$signup_method)

```
<br>
Distribution of Signup method
<br>
```{r}
ggplot(data, aes(x=signup_method)) +
  geom_bar(aes(fill=signup_method))
```
<br>
Distribution of age with respect to signup_method
<br>
```{r}
plt2 = ggplot(age_filtered,aes(x=age,na.rm=TRUE))+
  stat_density(aes(fill=signup_method))+
  scale_fill_brewer(palette="Dark2")+
  ggtitle("Distribution of Age with respect to Signup-method")+
  theme(plot.title = element_text(hjust=0.5))
grid.arrange(plt1,plt2,nrow=2,ncol=1)
```

```{r}
# Column
unique(data$language)
```

```{r}
# Distribution of Languages
ggplot(data, aes(x=language)) +
  geom_bar()

```

```{r}
#From the above bar plot, we can infer that the most of the data is for a single
#language, that is English

# Checking column affiliate_channel
unique(data$affiliate_channel)

# Checking column affiliate_provider
unique(data$affiliate_provider)
```
<br>
Distribution affiliate_channel
<br>
```{r}
#Distribution affiliate_channel
plt1= ggplot(data, aes(x=affiliate_channel)) +
  geom_bar(aes(fill=signup_method),color='black',position="dodge")+
  ggtitle("Distribution of Channel with respect to SignUp method")+
  ylab("Count")+
  xlab("Affiliate Channel")+
  theme(plot.title = element_text(hjust=0.5))
```
<br>
Distribution affiliate_provider
<br>
```{r}
#Distribution affiliate_provider
plt2 = ggplot(data, aes(x=affiliate_provider)) +
  geom_bar(aes(fill=signup_method),color='black',position="dodge")+
  ggtitle("Distribution of Provider with respect to SignUp method")+
  ylab("Count")+
  xlab("Affiliate Provider")+
  theme(plot.title = element_text(hjust=0.5),axis.text.x = element_text(angle=30,vjust=0.8))

grid.arrange(plt1,plt2,nrow=2,ncol=1)
```

```{r}
# Column - first_affiliate_tracked
# Checking column first_affiliate_tracked

unique(data$first_affiliate_tracked)

# Plotting barplot for different levels of column first_affiliate_tracked in data
plt1 = data %>% 
  filter(first_affiliate_tracked != "") %>% 
  ggplot(aes(x=first_affiliate_tracked)) +
  geom_bar(aes(fill=signup_method))+
  ggtitle("First marketing user interacted before SignUp")+
  ylab("Count")+
  xlab("First Affiliate")+
  theme(plot.title = element_text(hjust=0.5))
```

```{r}
# Checking column signup_app
unique(data$signup_app)

# Plotting barplot for different levels of sign_up in data
plt2 = ggplot(data=data,aes(x=signup_app)) +
  geom_bar(aes(fill=signup_method))+
  ggtitle("Application used for signup")+
  ylab("Count")+
  xlab("Application type")+
  theme(plot.title = element_text(hjust=0.5))
grid.arrange(plt1,plt2,nrow=2,ncol=1)
```
<br>
### CHI Squared Analysis 

Here we have performed an analysis to determine the nature dependency of categorical variables on each other. Since most of the features are categorical Chi squared analysis is a good fit. Chi Squared analysis is used to determine if two or more categorical features are related to each other. In this analysis, we perform a hypothesis test. If the p-value of the hypothesis test is less than 0.05, then we reject our Null hypothesis, otherwise, we cannot reject it.

#### Null Hypothesis: 
There is no relation between method used to signup and the type of app
<br>
#### Alternate Hypothesis: 
There is some relation between method used to signup and the type of app
<br>
#### Significance Level: 0.05
<br>
```{r}
data$signup_method = factor(data$signup_method)
data$signup_app = factor(data$signup_app)

contigency_table = table(data$signup_method,data$signup_app)
chisq.test(contigency_table)
```
<br>
Here, p-value is 2.2e-16, which is lower than 0.05 (significance level). Hence we can reject the null hypothesis and infer that there is some relation between the features signup_app and signup_method.
<br>


<br>
Distribution of feature first_browser
<br>
```{r}
# Checking column first_browser
str(data$first_browser)

# Checking summary of first_browser column
summary(data$first_browser)

# Plotting barplot for different levels of column first_browser in data
ggplot(data, aes(x=first_browser)) +
  geom_bar()

```
<br>
Distribution of destination country
<br>
```{r}
# Checking column country_destination
str(data$country_destination)

# Checking summary of country_destination column
summary(data$country_destination)

# Plotting barplot for different levels of column country_destination in data
ggplot(data, aes(x=country_destination)) +
  geom_bar()
```

<br>
Bi-variate analysis of features
<br>

```{r}
# Defining function for two categorical column visualization
bivariate <- function(arg_1, arg_2) {
  count <- table(arg_1, arg_2)
  barplot(count,beside = TRUE,legend.text = TRUE)
}
```

<br>
Gender vs. Country Destination
<br>

```{r}
# Plotting two categorical columns
bivariate(data$gender, data$country_destination)
```

<br>
Signup method vs. Country Destination
<br>

```{r}
# Plotting two categorical columns
bivariate(data$signup_method, data$country_destination)

```

<br>
Signup_flow vs Country Destination
<br>

```{r}
# Plotting two categorical columns
bivariate(data$signup_flow, data$country_destination)

```


### CONCLUSION 

Because we now know who to target and what kind of hotel is best for the users, our analysis helped us learn more about the demographic makeup of the users and their appropriate choices when they make a reservation on Airbnb. Our system will be able to distribute more personalized material within the community to be more predictive, reduce the average time towards first booking, and better forecast demand by accurately predicting where a new user will book their first hotel experience.

##### Github Link - https://github.com/shivam360d/DTSC-5301-Project-Report
##### By - Shivam Vats, Sushil Deore and Ansh Sachdeva 


